The Form of Uncertainty Affects Selection for Social Learning

### 2023-02-21 ms.tex

\begin{figure}
  \caption{Social learning goes extinct for larger values of environmental variability (SL extinction
    varibility, y-axis) as the number of
  behaviors afforded by the environment increases (x-axis).}
  \label{fig:extinctionVariability}
  \centering
    \includegraphics[width=0.8\textwidth]{Figures/SL_Extinction_Variability.pdf}
\end{figure}

>>>>

\begin{figure}
  \caption{As the number of
  behaviors afforded by the environment increases (x-axis), 
  social learning is supported up to increasingly large values of environmental variability (SL extinction
    varibility, y-axis).}
  \label{fig:extinctionVariability}
  \centering
    \includegraphics[width=0.8\textwidth]{Figures/SL_Extinction_Variability.pdf}
\end{figure}
